3D-printable micropipette

### 2015-01-26 publishing/plos_template.tex
methods draft finished

The pipette was validated and compared to a commerical pipette. 
The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.

>>>>

The pipette was validated and compared to a commerical pipette. 
The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.
The printed pipette and a series of commericial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L.
The printed pipette was adjusted to the the target volume by eye from the syring graduations, and the resulting volume was measured and repeated 5 times to account for varibility.
Measurment were taken from the commericial pipette in a similar way.

To test user friendliness and feasibilty for useing the pipette without verifing with a scale, data was also gathered from novice users.
After a quick overview of the opperation of the pipette measurments were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
After the first attempt was measured on the scale the volunteer was allow to adjust the set point and re-measure untill within 15\% of the target volume was reached.
